---
title: "HW09: Analyzing Hadestown"
author: "Julia Du"
date: "`r lubridate::today()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## Load necessary libraries

```{r, message = FALSE}
library(tidyverse)
#library(geniusr)
library(genius) #even easier than geniusr
library(scales)

library(tidytext)
library(widyr)
library(ggraph)
library(igraph)

library(viridis)
library(ggtext)
theme_set(theme_minimal())
set.seed(123)
```

## Get lyric data

I'm focusing on the musical *Hadestown* for most of my analysis, but I bring in *Les Miserables* and *Phantom of the Opera* at the end to look at common words between those 2 musicals and *Hadestown*.

I got the data From [Genius.com](https://genius.com) by using a very helpful package called `genius` (documentation [here](https://github.com/JosiahParry/genius)), so I didn't even have to get an API authentication token like with the `geniusr` package.

```{r, cache = TRUE}
hadestown <- genius_album(artist = "Anais Mitchell", album = "Hadestown (Original Broadway Cast Recording)")

phantom <- genius_album(artist = "Andrew Lloyd Webber", album = "The Phantom of the Opera (Original London Cast Recording)")

lesmis <- genius_album(artist = "Les Miserables Original Broadway Cast", album = "Les Miserables (1987 Original Broadway Cast)")
```

## Sentiment analysis

The following draws heavily from the example found [here](https://cfss.uchicago.edu/notes/hamilton/#pairs-of-words).

```{r}
string_hades <- hadestown %>%  
  pull(track_title) %>%
  str_remove(pattern = " by.*")

tidy_musical <- function(musical_df){
  # keep only song names w/o "by..." info
  clean_track_title <- musical_df %>%
    pull(track_title) %>%
  str_remove(pattern = " by.*")
  
  musical_df %>%
  bind_cols(clean_track_title) %>%
  select(-track_title) %>%
  rename(track_title = ...5) %>%
  mutate(track_title = as_factor(track_title)) %>%
# now tokenize
  unnest_tokens(output = word, input = lyric) %>%
  anti_join(stop_words)
}

tidy_hades <- tidy_musical(hadestown)

hadestown_tidy <- hadestown %>%
  bind_cols(string_hades) %>%
  select(-track_title) %>%
  rename(track_title = ...5) %>%
  mutate(track_title = as_factor(track_title)) %>%
# now tokenize
  unnest_tokens(output = word, input = lyric) %>%
  anti_join(stop_words)

hadestown_afinn <- hadestown_tidy %>%
  inner_join(get_sentiments(lexicon = "afinn")) %>%
  mutate(cum_sent = cumsum(value), id = row_number())

hadestown_afinn %>%
  group_by(track_title) %>%
  summarize(sent = mean(value)) %>%
  ggplot(mapping = aes(x = fct_rev(track_title), y = sent, fill = sent)) +
  geom_col() +
  scale_fill_viridis_c() +
  coord_flip() +
  labs(
    title = "Positive/negative sentiment in *Hadestown*",
    subtitle = "By song",
    x = NULL,
    y = "Average sentiment",
    fill = "Average\nsentiment",
    caption = "Source: Genius"
  ) +
  theme(plot.title = element_markdown(),
        legend.position = "none")
```

## adjust figure size!

```{r, fig.height = 10}
ggplot(data = hadestown_afinn, mapping = aes(x = id, y = cum_sent)) +
  geom_line() +
  scale_x_reverse(breaks = hadestown_afinn %>%
                    group_by(track_n) %>%
                    filter(id == min(id)) %>%
                    pull(id),
                  labels = hadestown_afinn %>%
                    group_by(track_n) %>%
                    filter(id == min(id)) %>%
                    pull(track_title)) +
  labs(
    title = "Positive/negative sentiment in *Hadestown*",
    x = NULL,
    y = "Cumulative sentiment",
    caption = "Source: Genius"
  ) +
  coord_flip() +
  theme(panel.grid.minor.y = element_blank(),
        plot.title = element_markdown())
```

We see some 

## Correlated words

same source as Markle file: https://www.tidytextmining.com/ngrams.html


```{r}
custom_hades <- c("la", "gonna")

custom_hades_stop <- bind_rows(tibble(word = custom_hades, lexicon = c("custom")), stop_words)


hades_cors <- hadestown_tidy %>%
  anti_join(custom_hades_stop) %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(item = word, feature = track_n, sort = TRUE)
# looking at the common pairs of words co-appearing w/in each article (as defined by recent_order)

hades_cors %>%
  filter(item1 %in% c("hell", "love", "song", "livin", "gotta", "wait")) %>%
  group_by(item1) %>%
  slice_head(n = 5) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(mapping = aes(x = item2, y = correlation)) +
  geom_col() +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()

hades_cors %>%
  filter(correlation > .35) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "orangered3", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  ggtitle("Word pairs with at least a correlation of .35 appearing in the same song")
```

## Comparing word frequencies

https://www.tidytextmining.com/tidytext.html

```{r}
library(tidyverse)
#library(geniusr)
library(genius) #even easier than geniusr
library(scales)
library(tidytext)

theme_set(theme_minimal())


hadestown <- genius_album(artist = "Anais Mitchell", album = "Hadestown (Original Broadway Cast Recording)")

phantom <- genius_album(artist = "Andrew Lloyd Webber", album = "The Phantom of the Opera (Original London Cast Recording)")

lesmis <- genius_album(artist = "Les Miserables Original Broadway Cast", album = "Les Miserables (1987 Original Broadway Cast)")

string_hades <- hadestown %>%  
  pull(track_title) %>%
  str_remove(pattern = " by.*")

hadestown_tidy <- hadestown %>%
  bind_cols(string_hades) %>%
  select(-track_title) %>%
  rename(track_title = ...5) %>%
  mutate(track_title = as_factor(track_title)) %>%
# now tokenize
  unnest_tokens(output = word, input = lyric) %>%
  anti_join(stop_words)

# above is for reprex purposes
string_phan <- phantom %>%  
  pull(track_title) %>%
  str_remove(pattern = " by.*")

phantom_tidy <- phantom %>%
  bind_cols(string_phan) %>%
  select(-track_title) %>%
  rename(track_title = ...5) %>%
  mutate(track_title = as_factor(track_title)) %>%
  unnest_tokens(output = word, input = lyric) %>%
  anti_join(stop_words)

string_lesmis <- lesmis %>%
  pull(track_title) %>%
  str_remove(pattern = " by.*")

lesmis_tidy <- lesmis %>%
  bind_cols(string_lesmis) %>%
  select(-track_title) %>%
  rename(track_title = ...5) %>%
  mutate(track_title = as_factor(track_title)) %>%
  unnest_tokens(output = word, input = lyric) %>%
  anti_join(stop_words)

# compare words in Hadestown to Phantom of the Opera & Les Mis
frequency <- bind_rows(mutate(hadestown_tidy, musical = "Hadestown"),
                       mutate(phantom_tidy, musical = "Phantom of the Opera"),
                       mutate(lesmis_tidy, musical = "Les Miserables")) %>% 
  count(musical, word) %>%
  group_by(musical) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>%
  pivot_wider(names_from = musical, values_from = proportion) %>%
  pivot_longer(c("Phantom of the Opera", "Les Miserables"), 
               names_to = "musical", values_to = "proportion")


# plot
frequency %>%
  ggplot(mapping = aes(x = proportion, y = `Hadestown`, 
                       color = abs(`Hadestown` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent) +
  scale_y_log10(labels = percent) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkolivegreen4", high = "firebrick") +
  #QUESTION IS HERE!!!
  facet_wrap(~ musical) +
  theme(legend.position="none") +
  labs(y = "Hadestown", x = NULL)
```    

"Words that are close to the line in these plots have similar frequencies in both sets of texts, for example, in both Austen and Brontë texts (“miss”, “time”, “day” at the upper frequency end) or in both Austen and Wells texts (“time”, “day”, “brother” at the high frequency end). Words that are far from the line are words that are found more in one set of texts than another. For example, in the Austen-Brontë panel, words like “elizabeth”, “emma”, and “fanny” (all proper nouns) are found in Austen’s texts but not much in the Brontë texts, while words like “arthur” and “dog” are found in the Brontë texts but not the Austen texts. In comparing H.G. Wells with Jane Austen, Wells uses words like “beast”, “guns”, “feet”, and “black” that Austen does not, while Austen uses words like “family”, “friend”, “letter”, and “dear” that Wells does not."

## Session info

```{r, echo = TRUE}
devtools::session_info()
```
